### 2020-07-17 paper/results.tex
After Osama's changes

The control rod parameters including control rod worth (CRW), interference 
between CR clusters, and integral and differential control rod worths are 
described in this part. 
Table~\ref{tab:worth} shows calculated CRW, the amplification 
factor (A$_{CRi}$), and the type of interference for six different 
absorbers.

\begin{sidewaystable}
	\fontsize{5}{7}\selectfont
	\centering
	\caption{The control rod worth and shadowing effect for different CR 
	materials.}
	\vspace{1ex}
	\begin{tabularx}{\textwidth}{|p{1.8cm}|p{0.56cm}|p{0.5cm}|p{0.49cm}|p{0.56cm}|p{0.5cm}|p{0.49cm}| 
	p{0.56cm}|p{0.5cm}|p{0.49cm}|p{0.56cm}|p{0.5cm}|p{0.49cm}| 
	p{0.56cm}|p{0.5cm}|p{0.49cm}|p{0.56cm}|p{0.5cm}|p{0.49cm}|}
		\hline
		\multirow{2}{*}{Control Rod group}		& 
		\multicolumn{3}{c|}{Nat. B$_4$C} & \multicolumn{3}{c|}{B$_4$C-90}   	&\multicolumn{3}{c|}{HfB$_2$}	
		&\multicolumn{3}{c|}{HfH$_{1.62}$} 
		&\multicolumn{3}{c|}{Gd$_2$O$_3$}	& 	
		\multicolumn{3}{c|}{Eu$_2$O$_3$} \\
		\cline{2-19}
		& $\Delta\rho$$_{CRi}$  [\$]  &A$_{CRi}$	& Inter\-ference
		& $\Delta\rho$$_{CRi}$  [\$]  &A$_{CRi}$	& Inter\-ference	
		&$\Delta\rho$$_{CRi}$ [\$]  &A$_{CRi}$	& Inter\-ference	
		&$\Delta\rho$$_{CRi}$ [\$]	&A$_{CRi}$	& Inter\-ference	
		&$\Delta\rho$$_{CRi}$ [\$]	&A$_{CRi}$	& Inter\-ference	
		&$\Delta\rho$$_{CRi}$ [\$]	&A$_{CRi}$  &	Inter\-ference \\
		\hline                   
		All control rods      &  $42.04\pm0.60$	&	&		& $48.19\pm0.68$   &	&	
		&$40.40\pm0.41$	&	&	&$37.96\pm0.36$	&	&	&$33.70\pm0.40$	&	
		&	&$42.39\pm0.48$	& &	 \\
		\hline 
		CSD 		 & $22.32\pm0.20$ 	& $1.24\pm0.01$	&	$\star$				& $25.50\pm0.23$   &$1.24\pm0.01$	&$\star$	&$21.90\pm0.17$	&$1.10\pm0.01$	&$\star$	&$20.62\pm0.34$	&$1.10\pm0.01$	&$\star$	&$18.48\pm0.25$	&$1.17\pm0.01$	&$\star$	&$22.96\pm0.18$	&$1.20\pm0.01$ &$\star$ \\
		\hline 
		SSD		   & $14.27\pm0.10$ 	&$1.38\pm0.02$	&	$\star$	&$16.39\pm0.11$ &$1.38\pm0.02$	&$\star$	&$14.27\pm0.21$	&$1.29\pm0.01$	&$\star$	&$13.23\pm0.18$	&$1.30\pm0.06$	&$\star$	&$12.00\pm0.20$	&$1.26\pm0.01$	&$\star$	&$14.58\pm0.11$	&$1.30\pm0.02$	&$\star$ \\
		\hline 
		CSD inner ring   &  $16.80\pm0.02$	&$1.50\pm0.01$	&$\star$ &  $18.42\pm0.05$  &$1.60\pm0.04$	&$\star$		&$16.29\pm0.29$	&$1.48\pm0.02$	&$\star$	&$15.50\pm0.17$	& $1.46\pm0.01$ &$\star$	&$14.12\pm0.07$	&$1.39\pm0.01$	&$\star$	&$16.92\pm0.13$	&$1.50\pm0.01$	 &$\star$\\
		\hline 
		CSD outer ring            &  $2.16\pm0.02$	&$3.11\pm0.06$	&	$\star$    &$2.26\pm0.02$ &$4.21\pm0.07$	&$\star$	&$2.10\pm0.06$	&$3.11\pm0.10$&$\star$	&$1.85\pm0.07$	&$3.24\pm0.06$	&$\star$	&$1.80\pm0.10$	&$2.54\pm0.14$	&$\star$	&$2.14\pm0.05$	&$3.20\pm0.05$	 &$\star$	\\
		\hline 
		CSD2			 &  $2.11\pm0.03$	&$3.00\pm0.08$	&	$\star$				& $2.25\pm0.04$   &$3.69\pm0.16$	&$\star$	&$2.24\pm0.05$	&$2.42\pm0.10$	&$\star$	&$2.00\pm0.10$	&$2.68\pm0.03$	&$\star$	&$1.80\pm0.10$	&$2.55\pm0.20$	&$\star$	&$2.19\pm0.12$	&$2.90\pm0.08$	&$\star$ \\
		\hline 
		CSD9			 &  $0.06\pm0.01$	&$15.16\pm0.10$	&	$\star$$\star$				& $0.15\pm0.04$   & $10.53\pm0.01$	&$\star$$\star$	&$0.10\pm0.05$	&$5.10\pm0.05$	&$\star$	&$0.05\pm0.01$	&$16.40\pm0.10$	&$\star$$\star$	&$0.09\pm0.07$	&$5.55\pm0.20$	&$\star$$\star$	&$0.07\pm0.05$	&$14.00\pm0.10$	&$\star$$\star$ \\ 
		\hline
		SSD1		 &  $3.95\pm0.05$	&$1.31\pm0.01$	&	$\star$		& $4.18\pm0.07$   &$1.59\pm0.08$	&$\star$	&$3.95\pm0.13$	&$1.30\pm0.07$	&$\star$	&$3.59\pm0.03$	&$1.49\pm0.01$	&$\star$	&$3.45\pm0.12$	&$1.40\pm0.08$	&$\star$	&$3.91\pm0.06$	&$1.40\pm0.01$&$\star$ \\
		\hline 
		SSD4		 &  $0.59\pm0.08$	& $9.52\pm0.10$	&	$\star$$\star$		&  $0.57\pm0.09$  &$7.84\pm0.15$	&$\star$$\star$	&$0.63\pm0.06$	&$4.40\pm0.10$	&$\star$	&$1.00\pm0.05$	&$2.51\pm0.16$	&$\star$	&$0.60\pm0.80$	&$3.31\pm0.27$	&$\star$	&$0.60\pm0.08$	&$5.10\pm0.28$	&$\star$$\star$ \\
		\hline
	\end{tabularx}
	\begin{tablenotes}
		\tiny
		\item  $\star$  anti-shadowing effects observed
		\item  $\star$$\star$ strong anti-shadowing effects observed
	\end{tablenotes}
	\label{tab:worth}
\end{sidewaystable}

\subsubsection{CRW} \label{CR_worth}

@@

The inner ring of the CSD is located in the central zone of the SD-TMSR core 
(Figure~\ref{fig:core_25}), in which the volume ratio between molten salt and 
graphite is relatively small ($0.357$). Results show that the inner ring of the CSD has 
a worth almost equal to the worth of all other CRs together (SSD + CSD outer ring) regardless of 
the absorbing material type (see Table~\ref{tab:worth}). This happens because the absorption cross section
decreases with the energy of the incident neutron; for example, boron absorbs neutrons in the thermal spectrum much 
greater than in the fast spectrum.

@@

The amplification factor (A$_{CRi}$) results show that the CSD, SSD, CSD inner 
ring, and SSD1 are slightly amplified due to the anti-shadowing effects. The 
anti-shadowing is observed when the combined rod worth is greater than the sum 
of the individual worths. The strongest anti-shadowing effect occurred in 
SSD4 and CSD9 clusters that are located at the boundary between the core zones 
with different moderator-to-fuel ratios (see Table~\ref{tab:worth}).
The obtained results emphasize that no relation exists between the absorbing
material type and the interference between the CR clusters
(i.e. the A$_{CRi}$).

@@

The differential CRWs are demonstrated in Figure~\ref{fig:diff}. Ideally, at the top of the core, the CR insertion has little effect since this region has low thermal neutron flux. Thus, the differential CRW has the lowest values in this region. The effect of CR insertion increases gradually near the center of the core. At the center of the core (region with maximum thermal neutron flux), the differential CRW is the largest and changes slowly with rod insertion. From the center of the core to the bottom, the differential CRW values decrease (region with low thermal neutron flux). Figure~\ref{fig:diff} shows that the maximum differential CRW is shifted toward the bottom of the core and the curves are not exactly symmetrical. This is due to the asymmetrical distribution of the fuel and graphite in simulation \cite{xuemei2013study,son2016control}.

>>>>

The control rod parameters including control rod worth (CRW), interference 
between CR clusters, and integral and differential control rod worths are 
described in this part. Table~\ref{tab:worth} shows calculated CRW and the amplification 
factor (A$_{CRi}$) for six different 
absorbers. The types of interference for all different 
absorbers are listed in Table ~\ref{tab:table25}. Fuel salt composition of LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$ at 70-17.5-12.3-0.2 mole\% is used to generate the results listed in Tables~\ref{tab:worth} and ~\ref{tab:table25}.
\begin{sidewaystable}
	\fontsize{5}{7}\selectfont
	\centering
	\caption{The control rod worth for different CR 
		materials.}
	\vspace{1ex}
	\begin{tabularx}{\textwidth}{|p{1.8cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}| 
			p{1cm}|p{1cm}|p{1cm}|p{1cm}| 
			p{1cm}|p{1cm}|p{1cm}|p{0.9cm}|}
		\hline
		\multirow{2}{*}{Control Rod group}		& 
		\multicolumn{2}{c|}{Nat. B$_4$C} & \multicolumn{2}{c|}{B$_4$C-90}   	&\multicolumn{2}{c|}{HfB$_2$}	
		&\multicolumn{2}{c|}{HfH$_{1.62}$} 
		&\multicolumn{2}{c|}{Gd$_2$O$_3$}	& 	
		\multicolumn{2}{c|}{Eu$_2$O$_3$} \\
		\cline{2-13}
		& $\Delta\rho$$_{CRi}$  [\$]  &A$_{CRi}$	
		& $\Delta\rho$$_{CRi}$  [\$]  &A$_{CRi}$		
		&$\Delta\rho$$_{CRi}$ [\$]  &A$_{CRi}$		
		&$\Delta\rho$$_{CRi}$ [\$]	&A$_{CRi}$		
		&$\Delta\rho$$_{CRi}$ [\$]	&A$_{CRi}$		
		&$\Delta\rho$$_{CRi}$ [\$]	&A$_{CRi}$  \\
		\hline                   
		All control rods      &  $42.04\pm0.60$	&	& $48.19\pm0.68$   &		
		&$40.40\pm0.41$	&		&$37.96\pm0.36$	&		&$33.70\pm0.40$	&	
			&$42.39\pm0.48$	& 	 \\
		\hline 
		CSD 		 & $22.32\pm0.20$ 	& $1.24\pm0.01$	 			& $25.50\pm0.23$   &$1.24\pm0.01$	 	&$21.90\pm0.17$	&$1.10\pm0.01$	 	&$20.62\pm0.34$	&$1.10\pm0.01$	 	&$18.48\pm0.25$	&$1.17\pm0.01$	 	&$22.96\pm0.18$	&$1.20\pm0.01$   \\
		\hline 
		SSD		   & $14.27\pm0.10$ 	&$1.38\pm0.02$	 	&$16.39\pm0.11$ &$1.38\pm0.02$	 	&$14.27\pm0.21$	&$1.29\pm0.01$	 	&$13.23\pm0.18$	&$1.30\pm0.06$	 	&$12.00\pm0.20$	&$1.26\pm0.01$	 	&$14.58\pm0.11$	&$1.30\pm0.02$	  \\
		\hline 
		CSD inner ring   &  $16.80\pm0.02$	&$1.50\pm0.01$	  &  $18.42\pm0.05$  &$1.60\pm0.04$	 		&$16.29\pm0.29$	&$1.48\pm0.02$	 	&$15.50\pm0.17$	& $1.46\pm0.01$  	&$14.12\pm0.07$	&$1.39\pm0.01$	 	&$16.92\pm0.13$	&$1.50\pm0.01$	  \\
		\hline 
		CSD outer ring            &  $2.16\pm0.02$	&$3.11\pm0.06$	     &$2.26\pm0.02$ &$4.21\pm0.07$	 	&$2.10\pm0.06$	&$3.11\pm0.10$ 	&$1.85\pm0.07$	&$3.24\pm0.06$	 	&$1.80\pm0.10$	&$2.54\pm0.14$	 	&$2.14\pm0.05$	&$3.20\pm0.05$	  	\\
		\hline 
		CSD2			 &  $2.11\pm0.03$	&$3.00\pm0.08$	 			& $2.25\pm0.04$   &$3.69\pm0.16$	 	&$2.24\pm0.05$	&$2.42\pm0.10$	 	&$2.00\pm0.10$	&$2.68\pm0.03$	 	&$1.80\pm0.10$	&$2.55\pm0.20$	 	&$2.19\pm0.12$	&$2.90\pm0.08$	  \\
		\hline 
		CSD9			 &  $0.06\pm0.01$	&$15.16\pm0.10$	 				& $0.15\pm0.04$   & $10.53\pm0.01$	  	&$0.10\pm0.05$	&$5.10\pm0.05$	 	&$0.05\pm0.01$	&$16.40\pm0.10$	  	&$0.09\pm0.07$	&$5.55\pm0.20$	  	&$0.07\pm0.05$	&$14.00\pm0.10$	  \\ 
		\hline
		SSD1		 &  $3.95\pm0.05$	&$1.31\pm0.01$	 	& $4.18\pm0.07$   &$1.59\pm0.08$	 	&$3.95\pm0.13$	&$1.30\pm0.07$	 	&$3.59\pm0.03$	&$1.49\pm0.01$	 	&$3.45\pm0.12$	&$1.40\pm0.08$	 	&$3.91\pm0.06$	&$1.40\pm0.01$  \\
		\hline 
		SSD4		 &  $0.59\pm0.08$	& $9.52\pm0.10$	 		&  $0.57\pm0.09$  &$7.84\pm0.15$	 	&$0.63\pm0.06$	&$4.40\pm0.10$	 	&$1.00\pm0.05$	&$2.51\pm0.16$	 	&$0.60\pm0.80$	&$3.31\pm0.27$	 	&$0.60\pm0.08$	&$5.10\pm0.28$	  \\
		\hline
	\end{tabularx}
	\label{tab:worth}
\end{sidewaystable}

\begin{sidewaystable}
	\fontsize{5}{7}\selectfont
	\centering
	\caption{The shadowing effect for different CR materials.}
	\vspace{0.1in}
		\begin{tabularx}{\textwidth}{|X|X|X|X|X|X|X|}
		\hline
		\multirow{2}{*}{Control Rod group}		& Nat. B$_4$C & B$_4$C-90  	&HfB$_2$
		&HfH$_{1.62}$
		&Gd$_2$O$_3$& 	
		Eu$_2$O$_3$ \\
		\cline{2-7}
		&  Interference
		& Interference	
		& Interference	
		& Interference	
		& Interference
		& Interference \\
		\hline                   
	CSD 		&	$\star$				& $\star$	&$\star$		&$\star$		&$\star$  &$\star$	 \\
	\hline 
	SSD		   &	$\star$				& $\star$	&$\star$		&$\star$		&$\star$  &$\star$	 \\ 
	\hline 
	CSD inner ring   &  	$\star$				& $\star$	&$\star$		&$\star$		&$\star$  &$\star$	 \\
	\hline 
	CSD outer ring       &	$\star$				& $\star$	&$\star$		&$\star$		&$\star$  &$\star$	 \\     
	\hline 
	CSD2			&	$\star$				& $\star$	&$\star$		&$\star$		&$\star$  &$\star$	 \\  
	\hline 
	CSD9		&	$\star$$\star$				& $\star$$\star$	&$\star$		&$\star$$\star$			&$\star$$\star$	  &$\star$$\star$		 \\ 	 
	\hline
	SSD1	&	$\star$				& $\star$	&$\star$		&$\star$		&$\star$  &$\star$ \\	  
	\hline 
	SSD4		&		$\star$$\star$			& 	$\star$$\star$	&$\star$		&$\star$		&$\star$  &	$\star$$\star$	 \\  
	\hline
	\end{tabularx}
	\begin{tablenotes}
	\tiny
	\item  $\star$  anti-shadowing effects observed
	\item  $\star$$\star$ strong anti-shadowing effects observed
\end{tablenotes}
	\label{tab:table25}
\end{sidewaystable}
\subsubsection{CRW} \label{CR_worth}

@@

The inner ring of the CSD is located in the central zone of the SD-TMSR core 
(Figure~\ref{fig:core_25}), in which the volume ratio between molten salt and 
graphite is relatively small ($0.357$). Results show that the inner ring of the CSD has 
a worth almost equal to the worth of all other CRs together (SSD + CSD outer ring) regardless of 
the absorbing material type (see Table~\ref{tab:worth}). This happens because the absorption cross section
decreases with the energy of the incident neutron; for example, boron absorbs neutrons in the thermal spectrum much 
greater than in the fast spectrum. Additionally, the maximum neutron flux is located in the central zone of the SD-TMSR (see Figure~\ref{fig:totalflux}); therefore the inner ring of the CSD has a worth higher than the worth of the outer ring of the CSD.

@@

The amplification factor (A$_{CRi}$) results show that the CSD, SSD, CSD inner 
ring, and SSD1 are slightly amplified due to the anti-shadowing effects. The 
anti-shadowing is observed when the combined rod worth is greater than the sum 
of the individual worths. As listed in Tables~\ref{tab:worth} and ~\ref{tab:table25}, the strongest anti-shadowing effect occurred in 
SSD4 and CSD9 clusters that are located at the boundary between the core zones 
with different moderator-to-fuel ratios. This can be attributed to the fact that the SSD4 and CSD9 clusters are surrounded by fewer clusters compared with other clusters located in the inner zone of the SD-TMSR (see Figure~\ref{fig:core_25}). Consequently, low interference between the SSD4 and CSD9 clusters and other surrounding clusters is observed. The obtained results show a negligible relationship between the absorbing material type and the interference between the CR clusters (i.e. the A$_{CRi}$).

@@

The differential CRWs are demonstrated in Figure~\ref{fig:diff}. Theoretically, at the top of the core, the CR insertion has little effect since this region has low thermal neutron flux. Thus the differential CRW has the lowest values in this region. The effect of CR insertion increases gradually near the center of the core. At the center of the core (region with maximum thermal neutron flux), the differential CRW is the largest and changes slowly with rod insertion. From the center of the core to the bottom, the differential CRW values decrease (region with low thermal neutron flux). Figure~\ref{fig:diff} shows that the maximum differential CRW is shifted toward the bottom of the core and the curves are not exactly symmetrical. This is due to the asymmetrical distribution of the fuel and graphite in simulation \cite{xuemei2013study,son2016control}.
